---
title: "The Mother of all RMarkdown Files"
author: "Falk Mielke"
date: "2024-09-03"
output: md_document
---

<!-- https://stackoverflow.com/questions/40717410/opts-knitsetroot-dir-path-does-not-work-after-rstudio-upgrade-1-0-44 -->


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
print(here::here())
print(rprojroot::find_root(rprojroot::is_rstudio_project))
knitr::opts_knit$set(root.dir = normalizePath(rprojroot::find_root(rprojroot::is_rstudio_project)))
knitr::opts_chunk$set(root.dir = normalizePath(rprojroot::find_root(rprojroot::is_rstudio_project)))
```

# Conventional Navigation
With the help of `rprojroot`, we can find the root folder of the package.

```{r}
require('rprojroot')
find_root(is_rstudio_project)
```


Let's use a function to print the current directory and the content of a `location.txt` file.

```{r}
CheckDirectory <- function () {
  print(getwd()) # display the working directory
  
  fi = 'location.txt'
  if (file.exists(fi)) {
    print(readLines(fi))
  }
}

CheckDirectory()
```


Attempt to walk to the "source" subfolder:
```{r}
tryCatch(
{setwd('source')
CheckDirectory()},
        error = function(cond) {
            message(paste('error:', conditionMessage(cond)))
            return(NA)
        }
)

```
This gives a warning:
> Warning: The working directory was changed to /data/R/wd_testing/source inside a notebook chunk. 
> The working directory will be reset when the chunk is finished running.
> Use the knitr root.dir option in the setup chunk to change the working directory for notebook chunks.


... and then to the "data" subfolder:
```{r}
tryCatch(
{setwd('../data')
CheckDirectory()},
        error = function(cond) {
            message(paste('error:', conditionMessage(cond)))
            return(NA)
        }
)
```


Finally, back to the roots:
```{r}
setwd('..')
CheckDirectory()
```

(... this is unexpected; I would not want to walk out of the project folder.)


Go back to the root:
```{r}
setwd(find_root(is_rstudio_project))
```

# Using the `here` Package
I found [https://here.r-lib.org](this) on reddit:

```{r}
require('here')
here()
```

```{r}
here('source', 'location.txt')
```
